\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[T1]{fontenc}
\usepackage{beramono}
\usepackage{jlcode}

%%
%% Julia definition (c) 2014 Jubobs
%%
% \lstdefinelanguage{Julia}%
%   {morekeywords={abstract,break,case,catch,const,continue,do,else,elseif,%
%       end,export,false,for,function,immutable,import,importall,if,in,%
%       macro,module,otherwise,quote,return,switch,struct,true,try,type,typealias,%
%       using,while},%
%    sensitive=true,%
%    alsoother={$},%
%    morecomment=[l]\#,%
%    morecomment=[n]{\#=}{=\#},%
%    morestring=[s]{"}{"},%
%    morestring=[m]{'}{'},%
% }[keywords,comments,strings]%

% \lstset{%
%     language         = Julia,
%     basicstyle       = \ttfamily,
%     keywordstyle     = \bfseries\color{blue},
%     stringstyle      = \color{magenta},
%     commentstyle     = \color{ForestGreen},
%     showstringspaces = false,
% }

\begin{document}

\section*{Mathematical Formulation of the LPProblem}

Given a linear programming problem, we aim to either minimize or maximize a linear objective function subject to a set of linear constraints.

Let:
\begin{itemize}
    \item $\mathbf{c} \in \mathbb{R}^n$ be the vector of objective function coefficients.
    \item $\mathbf{A} \in \mathbb{R}^{m \times n}$ be the constraint matrix.
    \item $\mathbf{b} \in \mathbb{R}^m$ be the vector representing the right-hand side of the constraints.
    \item $\mathbf{l} \in \mathbb{R}^n$ be the vector of lower bounds for the variables.
    \item $\mathbf{u} \in \mathbb{R}^n$ be the vector of upper bounds for the variables.
    \item $\mathbf{x} \in \mathbb{R}^n$ be the vector of decision variables.
    \item $\text{vars} = \{x_1, x_2, \dots, x_n\}$ be the variable names.
    \item $\text{constraint\_types} = \{c_1, c_2, \dots, c_m\}$ where $c_i \in \{\leq, \geq, =\}$ represents the type of each constraint.
\end{itemize}

The general mathematical formulation is as follows:

\subsection*{Objective Function}
\[
\text{Minimize or Maximize:} \quad \mathbf{c}^\top \mathbf{x}
\]
depending on the value of \texttt{is\_minimize} (if True, minimize; if False, maximize).

\subsection*{Constraints}
\[
\mathbf{A} \mathbf{x} \begin{cases} 
\leq \mathbf{b}, & \text{if } c_i = \leq \\
\geq \mathbf{b}, & \text{if } c_i = \geq \\
= \mathbf{b}, & \text{if } c_i = = \\
\end{cases} \quad \text{for } i = 1, 2, \dots, m
\]

\subsection*{Variable Bounds}
\[
\mathbf{l} \leq \mathbf{x} \leq \mathbf{u}
\]

where $\mathbf{x} = \{x_1, x_2, \dots, x_n\}$ are the decision variables, and the bounds are element-wise.



\section*{Code Formulation}

\begin{jllisting}
    struct LPProblem
        is_minimize::Bool  # True if the objective is to minimize
        c::Vector{Float64}  # Objective function coefficients
        A::SparseMatrixCSC{Float64, Int64}  # Constraint matrix
        b::Vector{Float64}  # Right-hand side of constraints
        l::Vector{Float64}  # Variable lower bounds
        u::Vector{Float64}  # Variable upper bounds
        vars::Vector{String}  # Variable names
        constraint_types::Vector{Char}  # Constraint types
    end
\end{jllisting}

\end{document}